MsCcHSFeed Outline

### 2022-01-18 MsCcHSFeedOutlineDec15.Rmd
Edited to do correct binomial calculations
Added new wasp survival figure and analyses, relabeled other figure numbers!

# Fig 2: Violin plots of max mass

@@

# Fig 3: Developmental outcome proportions

@@

# Fig 4: Maximum mass and age

@@

# Fig 5: Leaf matter consumed vs. max mass

@@

```{r}
binomWOWE <- data %>%
  select(ID, food, fate)

@@

```{r}
binomWE <- data %>%
  select(ID, food, fate)

@@

summary(we)
```

>>>>

# Fig 2: Wasp survival across plant types

```{r}
datawasp <- data[data$para == "yes", ] %>%
  select(ID, food, treatment, num.w.coc, num.w.larvae, num.w.eclos)

datawasp <- datawasp[complete.cases(datawasp), ]

datawasp$num.w.tot <- datawasp$num.w.coc + datawasp$num.w.larvae
datawasp$percent <- (datawasp$num.w.eclos) / (datawasp$num.w.tot)
```

```{r}
waspplot <- ggplot(data = datawasp, aes(x = food, y = percent)) +
  theme_bw() + 
  geom_boxplot() + 
  geom_jitter(aes(color = treatment), width = 0.1, height = 0) + 
  labs(x = "Hostplant", y = "Percent survival from emergence to eclosion", color = "Treatment")

waspplot

ggsave("~/Desktop/waspplot.png", plot = waspplot, width = 8, height = 5)

## Statistics

```{r}
waspbinom <- glm(percent ~ food, family = "binomial", weights = num.w.tot, data = datawasp)

summary(waspbinom)

anova(waspbinom, test = "Chisq")

```{r}
waspbinom2 <- glm(percent ~ food, family = "binomial", weights = num.w.tot, 
                  data = datawasp[datawasp$treatment == "P NHS", ])

summary(waspbinom2)

anova(waspbinom2, test = "Chisq")

```{r}
waspemerge <- lm(num.w.tot ~ food, data = datawasp)

summary(waspemerge)
```

```{r}
waspemergetreat <- lm(num.w.tot ~ treatment, data = datawasp)

summary(waspemergetreat)
```

# Fig 3: Violin plots of max mass

@@

# Fig 4: Developmental outcome proportions

@@

# Fig 5: Maximum mass and age

@@

# Fig 6: Leaf matter consumed vs. max mass

@@

```{r}
binomWOWE <- data[data$treatment == "P HS", ] %>%
  select(ID, food, fate)

@@

```{r}
binomWE <- data[data$treatment == "P HS", ] %>%
  select(ID, food, fate)

@@

summary(we)

anova(we, test = "Chisq")
```
